Smart Drill-Down

### 2014-11-29 TableSummarization/Paper/TableSummarization.tex
small length reduction changes
small changes for length

\usepackage{floatrow}
\floatsetup[table]{font=scriptsize}

@@

@@

\title{Smart Drill-Down}
\numberofauthors{3} 
\author{
\alignauthor
Manas Joglekar\\
       \affaddr{Stanford University}\\
       \affaddr{353 Serra Mall}\\
	   \affaddr{Stanford, California 94305}\\
       \email{manasrj@stanford.edu}
\alignauthor
Hector Garcia-Molina\\
       \affaddr{Stanford University}\\
       \affaddr{353 Serra Mall}\\
	   \affaddr{Stanford, California 94305}\\
       \email{hector@cs.stanford.edu}
\alignauthor 
Aditya Parameswaran\\
       \affaddr{University of Illinois at Urbana-Champaign}\\
       \affaddr{Champaign, Illinois 61820}\\
       \email{adityagp@illinois.edu}
}
\maketitle

\begin{abstract}
In this paper we present {\em smart drill down},
an operator for interactively exploring a relational table
to discover ``interesting'' groups of tuples.
Each group of tuples is described by a {\em rule}.
For instance, the rule $(a, b, \star, 1000)$ tells us that
there are a $1000$ tuples with value $a$ in the first column and $b$
in the second column (and any value in the third column).
Smart drill down presents an analyst with a list of rules that
together describe interesting aspects of the table.
The analyst can tailor the definition of interesting,
and can interactively apply smart drill down on an existing rule to
explore that part of the table.
We describe an
algorithm for finding the approximately optimal list of rules to display when the user uses a smart drill down, and a dynamic sampling scheme for efficiently dealing with large tables. Finally, we
perform experiments on real datasets to demonstrate the usefulness of smart drill down and to study the performance of our algorithms.
\end{abstract}

@@

\bibliographystyle{abbrv}
\bibliography{TableSummarization}

>>>>

% \usepackage{floatrow}
% \floatsetup[table]{font=scriptsize}
% \renewcommand\FBbskip{-10pt}

@@

\makeatletter
\def\@copyrightspace{\relax}
\makeatother

@@

\title{Smart Drill-Down}
\numberofauthors{3} 
\author{
\alignauthor
Manas Joglekar\\
       \affaddr{Stanford University}\\
%       \affaddr{353 Serra Mall}\\
%	   \affaddr{Stanford, California 94305}\\
       \email{manasrj@stanford.edu}
\alignauthor
Hector Garcia-Molina\\
       \affaddr{Stanford University}\\
%       \affaddr{353 Serra Mall}\\
%	   \affaddr{Stanford, California 94305}\\
       \email{hector@cs.stanford.edu}
\alignauthor 
Aditya Parameswaran\\
       \affaddr{University of Illinois (UIUC)}\\
%       \affaddr{Champaign, Illinois 61820}\\
       \email{adityagp@illinois.edu}
}
\maketitle

\begin{abstract}
We present {\em smart drill-down},
an operator for interactively exploring a relational table
to discover and summarize ``interesting'' groups of tuples.
Each group of tuples is described by a {\em rule}.
For instance, the rule $(a, b, \star, 1000)$ tells us that
there are a thousand tuples with value $a$ in the first column and $b$
in the second column (and any value in the third column).
Smart drill-down presents an analyst with a list of rules that
together describe interesting aspects of the table.
The analyst can tailor the definition of interesting,
and can interactively apply smart drill-down on an existing rule to
explore that part of the table.
We demonstrate that the underlying optimization problems 
are {\sc NP-Hard}, and describe an
algorithm for finding the approximately optimal list of rules to display when the user uses a smart drill-down, and a dynamic sampling scheme for efficiently interacting with large tables. Finally, we
perform experiments on real datasets to demonstrate the usefulness of smart drill-down and study the performance of our algorithms.
\end{abstract}

@@

{\small
\bibliographystyle{abbrv}
\bibliography{TableSummarization}  
}

### 2014-11-29 TableSummarization/Paper/exp.tex
Added hinge loss, and clarified tree structure.
small changes for length

\begin{comment} ask about below:
Additional experiments:
Maybe also good to fix mw, and show the performance with or without sampling,
and with or without a-priori (one rule per phase, for instance).
Also, would be good to see performance on increasing dataset size.
\end{comment}

\subsection{Datasets}
The first dataset, denoted `Marketing', contains demographic information about potential customers. The source of the dataset is Impact Resources, Inc., Columbus, OH (1987). A total of $N=9409$ questionnaires containing $502$ questions were 
filled out by shopping mall customers in the San Francisco Bay area. This dataset is an extract from this survey. Each tuple in the data table describes a single person. There are $14$ columns, each of which is a demographic attribute, such as annual income, Gender, marital status, age, education, and so on. Continuous values, such as income, have been bucketized in the dataset, and thus each column has upto $10$ distinct values.

@@

\begin{table*} 
\centering 
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4918$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4075$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2940$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & > 10 years & $980$ & $3$ \\
\hline 
\end{tabular} 
\vspace{-15pt}
\caption{Summary after clicking on the empty rule \label{table:uiexample1}} 
\end{table*}

\begin{table*} 
\centering 
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4918$ & $1$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Female & $\star$ & $\star$ & High school & $\star$ & $\star$ & $1149$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Female & $\star$ & $\star$ & Grades 9-11 & $\star$ & $\star$ & $605$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Female & $\star$ & $\star$ & College graduate & $\star$ & $\star$ & $771$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Female & $\star$ & $\star$ & 1-3 years college & $\star$ & $\star$ & $1712$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4075$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2940$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & > 10 years & $980$ & $3$ \\
\hline 
\end{tabular} 
\vspace{-15pt}
\caption{Star expansion on 'Education' Column \label{table:uiexamplestar}} 
\end{table*}

\begin{table*} 
\centering 
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4918$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4075$ & $1$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & $\star$ & $1897$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Male & Married & $\star$ & $\star$ & $\star$ & $\star$ & $1368$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & > 10 years & $980$ & $3$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Male & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2242$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2940$ & $2$ \\
\hline 
\end{tabular} 
\vspace{-15pt}
\caption{A Rule expansion \label{table:uiexamplerule}} 
\end{table*}

@@

\begin{table*} 
\centering 
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $5182$ & $3$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\star$ & $\star$ & $\star$ & $\star$ & Professional / Managerial & $\star$ & $2820$ & $4$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\star$ & Never married & $\star$ & $\star$ & Student & > 10 years & $742$ & $10$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\star$ & Married & $\star$ & $\star$ & Professional / Managerial & > 10 years & $825$ & $10$ \\
\hline 
\end{tabular} 
\vspace{-15pt}
\caption{Bits scoring\label{table:weigtingbitwise}} 
\end{table*}

\begin{table*} 
\centering 
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2940$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & > 10 years & $980$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & Married & $\star$ & $\star$ & $\star$ & > 10 years & $1230$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & Married & $\star$ & $\star$ & $\star$ & > 10 years & $823$ & $2$ \\
\hline 
\end{tabular} 
\vspace{-15pt}
\caption{Size minus one weighting \label{table:weightingsizeminusone}} 
\end{table*}

@@

\begin{figure}
\hspace{-15pt}
  \includegraphics[height=2in]{graphs/mw_speed.pdf}%change height to 2 inch for actual paper, 5 inch for single column
\vspace{-5pt}
  \caption{Running time for different values of parameter $m_w$ \label{fig:mw_speed}}
\vspace{-15pt}
\end{figure}

@@

>>>>

\subsection{Datasets}
The first dataset, denoted `Marketing', contains demographic information about potential customers. The source of the dataset is Impact Resources, Inc., Columbus, OH (1987). A total of $N=9409$ questionnaires containing $502$ questions were 
filled out by shopping mall customers in the San Francisco Bay area. This dataset is an extract from this survey. Each tuple in the data table describes a single person. There are $14$ columns, each of which is a demographic attribute, such as annual income, Gender, marital status, age, education, and so on. Continuous values, such as income, have been bucketized in the dataset, and thus each column has upto $10$ distinct values. 
\begin{table*} 
\centering 
\scriptsize
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4918$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4075$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2940$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & > 10 years & $980$ & $3$ \\
\hline 
\end{tabular} 
\vspace{-10pt}
\caption{Summary after clicking on the empty rule \label{table:uiexample1}} 
\vspace{-10pt}
\end{table*}

\begin{table*} 
\centering 
\scriptsize
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4918$ & $1$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Female & $\star$ & $\star$ & High school & $\star$ & $\star$ & $1149$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Female & $\star$ & $\star$ & Grades 9-11 & $\star$ & $\star$ & $605$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Female & $\star$ & $\star$ & College graduate & $\star$ & $\star$ & $771$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Female & $\star$ & $\star$ & 1-3 years college & $\star$ & $\star$ & $1712$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4075$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2940$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & > 10 years & $980$ & $3$ \\
\hline 
\end{tabular} 
\vspace{-10pt}
\caption{Star expansion on 'Education' Column \label{table:uiexamplestar}} 
\vspace{-10pt}
\end{table*}

\begin{table*} 
\centering 
\scriptsize
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4918$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4075$ & $1$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & $\star$ & $1897$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Male & Married & $\star$ & $\star$ & $\star$ & $\star$ & $1368$ & $2$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & > 10 years & $980$ & $3$ \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\triangleright$ Male & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2242$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2940$ & $2$ \\
\hline 
\end{tabular} 
\vspace{-10pt}
\caption{A Rule expansion \label{table:uiexamplerule}} 
\vspace{-10pt}
\end{table*}

@@

@@

@@

\begin{figure}
%\hspace{-15pt}
\centering
  \includegraphics[scale=0.6]{graphs/mw_speed.pdf}%change height to 2 inch for actual paper, 5 inch for single column
\vspace{-5pt}
  \caption{Running time for different values of parameter $m_w$ \label{fig:mw_speed}}
\vspace{-15pt}
\end{figure}

@@

\begin{table*} 
\scriptsize
\centering 
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $5182$ & $3$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\star$ & $\star$ & $\star$ & $\star$ & Professional / Managerial & $\star$ & $2820$ & $4$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\star$ & Never married & $\star$ & $\star$ & Student & > 10 years & $742$ & $10$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ $\star$ & Married & $\star$ & $\star$ & Professional / Managerial & > 10 years & $825$ & $10$ \\
\hline 
\end{tabular} 
\vspace{-10pt}
\caption{Bits scoring\label{table:weigtingbitwise}} 
\vspace{-10pt}
\end{table*}

\begin{table*} 
\scriptsize
\centering 
\begin{tabular}{| p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | l | l |} 
\hline Gender & Marital Status & Age & Education & Occupation & Time in Bay Area & Count & Weight \\ \hline 
\cline{1-8} $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $8993$ & $0$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2940$ & $1$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & Never married & $\star$ & $\star$ & $\star$ & > 10 years & $980$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Female & Married & $\star$ & $\star$ & $\star$ & > 10 years & $1230$ & $2$ \\
\cline{1-1} \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-8} $\triangleright$ Male & Married & $\star$ & $\star$ & $\star$ & > 10 years & $823$ & $2$ \\
\hline 
\end{tabular}
\vspace{-10pt}
\caption{Size minus one weighting \label{table:weightingsizeminusone}} 
\vspace{-10pt}
\end{table*}
